### 2023-03-24 application.tex
details
up

@@

\subsection{Vector Addition System with States}

>>>>

\subsection{VASS, 2-VASS, semilinear VASS, Lossy Channel Systems, Integer et Continuous VASS, Regular Channel Systems}

\subsection{LCM}

\begin{theorem}{se déduit du papier Schnoebelen RP 2010, page 8}
Resilience is decidable for LCM when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

@@

\subsection{Vector Addition System with States or PN}
